



*text* or _text_ gives italic
**Bold**
3~rd gives the subscripting
3^rd gives you super

Hyperlinks [text](link)
^[this is a footnote]

**HEADERS**

# first-level Header

## Second-level header

### Thrid-level Header

# For numbering the headers add this {-}

# for unbumber {.unnumbered}

# Preface{-}

Indenting * - or +

> Block Quotes 
> -- Praveen

    Where all of this is coming from and I thought we are fine
    
```{r, chunk-label, results='hide', fig.height=4}

### eval: evaluates a code chunk
### echo: echo source code or not
### results: 'hide', 'asis'? idk

```

```{r}
### collapse: 'True' or "FALSE':make the output compact by merging the text output and source code into a single code block in the output
### include: 
### warning: FALSE
### message: FALSE
```
    
```{r}
### fig.width; fig.height; in single option = fig.dim = c(3,2); width followed by height.
```

```{r}
### out.width; out.height is for output width and height in percentatges
### fig.aligh: left center or right
### dev: record r plots: pdf for latex, png for html, svg or jpeg
### fig.cap: caption for figure
### child: opens child document and Idk wtf this is;
```


- To use certain option multiple times we can use it initially

```{r, setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 6, collapse = TRUE)

```

- Figures

```{r}
par(mar = c(4,4,0.2,0.1))
plot(cars, pch = 19)
plot(pressure, pch = 17)
```

- Tables

```{r tables-mtcars}
knitr::kable(iris[1:5,], caption = 'A Caption')
```
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    